### 2021-01-03 paper/localpsf.tex
minor edits

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [CITE JACOBSEN], the function $w_i$ is the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

The most popular existing Hessian approximation methods are based on forming a low rank approximation of the data misfit term in the Hessian, or the data misfit term preconditioned by the prior term [CITE LOTS OF STUFF]. Either the Lanczos method or the randomized singular value decomposition [CITE RSVD] are used to perform the low rank approximation using only matrix-vector products. These methods suffer from a ``data predicament''---as more informative data is used in the inversion, the numerical rank of the data misfit term in the Hessian grows, so more matrix-vector products are required to form the aforementioned low rank approximation. The ideal scenario from a scientific perspective (highly informative data) is the worst case scenario from a computational perspective (large computational cost) [CITE MY DISSERTATION]. The method in this paper offers a \emph{data-scalable} alternative to conventional low-rank Hessian approximation methods, because high-rank approximations of an operator can be formed using a small number of matrix-vector products.

>>>>

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [CITE JACOBSEN], the function $w_i$ is the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation [CITE ESCANDE ETC], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

The most popular existing Hessian approximation methods are based on forming a low rank approximation of the data misfit term in the Hessian, or the data misfit term preconditioned by the prior term [CITE LOTS OF STUFF]. Either the Lanczos method or the randomized singular value decomposition [CITE RSVD] are used to perform the low rank approximation using only matrix-vector products. These methods suffer from a ``data predicament''---as more informative data is used in the inversion, the numerical rank of the data misfit term in the Hessian grows, so more matrix-vector products are required to form the aforementioned low rank approximation. The ideal scenario from a scientific perspective (highly informative data) is the worst case scenario from a computational perspective (large computational cost) [CITE MY DISSERTATION]. Although the method we present in this paper is not applicable to all Hessians, it is applicable to several Hessians of practical interest. For these Hessians, our method offers a \emph{data-scalable} alternative to conventional low-rank Hessian approximation methods, because high-rank approximations of an operator can be formed using a small number of matrix-vector products.
